### 2022-02-18 paper/output/document/thesis_3_implementation.tex
started chapter 4

The central unit of evaluation for Kantian ethics is a ``maxim,'' which Kant defines as ``the subjective 
principle of willing,'' or the principle that the agent understands themselves as acting on \citep{groundwork}. 
Modern Kantians differ in their interpretations of this definition. I adopt O'Neill's view, derived from 
Kant's example maxims, that a maxim includes the act, the circumstances, and the agent's purpose of 
acting or goal \citep{actingonprinciple}.

@@

I implement this definition in Isabelle by defining the \texttt{type\_synonym} below for the type
of a maxim.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am strapped for cash, will falsely promise
to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
world when my bank account is empty. The second term represents the action, which is an open sentence
because different agents can perform a particular action. For example, the action, ``will falsely promise
to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
is true at the real world if I have successfully received easy cash.%
}%
\begin{isamarkuptext}%
O'Neill argues that a maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed \citep[37]{actingonprinciple}. 
She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
but instead in the pursuit of ends which it deems valuable.\footnote{Some argue that a maxim should also
include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.} The inclusion a maxim's end is essential for the version of the FUL
that I will implement, explained in Section \ref{praccon}.

\color{red} SHOULD THIS GO HERE OR IN THE LIMITATIONS SECTION OF THE DISCUSSION

O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
relevant circumstance for a particular maxim. This gives rise to ``the tailoring objection,'' 
under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.} For example, the maxim ``When my name is Jane Doe
and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job,'' 
is universalizable but is clearly a false positive because we think that murder for professional gain is wrong. 
One solution to this problem is to argue that the circumstance ``When my name is Jane Doe and I am wearing a 
purple shirt and it is Tuesday morning'' is not morally relevant 
to the act and goal. This solution requires determining what qualifies as a relevant circumstance.

@@

Another solution is to develop heuristics to classify circumstances as morally 
relevant. For example, one such attempt could define a moral closeness relation between an action, a 
goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
reach a certain closeness threshhold with the action and the goal. Determining morally relevant
circumstances, either using heuristics or human involvement, is a ripe area for future work.
\color{black}

@@

As an alternative to the logical contradiction view, Korsgaard endorses the practical contradiction view, 
which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
an agent commits themselves to the maxim's goal, and thus cannot rationally will that this goal be 
undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
loud children, then she cannot be secure in the possession of her life, because her own mother would 
have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
My above investigation of \texttt{FUL0} shows that if the FUL holds for badly formed maxims, then 
it is inconsistent. This is not only a logical property of my system, but it also has philosophical
significance that coheres with Korsgaard's and O'Neill's interpretations of a maxim as a practical
guide to action \citep{actingforareason,actingonprinciple}. A maxim is a practical principle that guides how we behave in everyday life. A 
principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast,'' is not 
practically relevant. No agent would ever need to act on such a principle. It is neither contradictory
nor prohibited, and it is the wrong kind of question to be asking. It is not a 
well-formed maxim, so the categorical imperative cannot apply to it.

@@

\includegraphics[scale=0.4]{goalstable.png}

@@

\noindent \textbf{Contradictory Obligations} Contradictory obligations

@@

for rational agents. Ought implies can requires that obligations never contradict, because an agent 

@@

\noindent \textbf{Distributive Property} Another property related to contradictory obligations is the distributive property for the obligation

@@

\noindent \textbf{Un-universalizable Actions} Recall that 
the logical contradiction interpretation of the Formula of Universal Law prohibits lying because in a world 
where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
lie because the institution of lying and believing would break down. In Section \ref{praccon}, 
I recreated Korsgaard's argument for why the logical contradiction interpretation is weaker than what the
Formula of Universal Law should actually require. Therefore, any implementation of the FUL should be 
able to show that the actions prohibited by the logical contradiction interpretation are prohibited, 
because the set of actions prohibited by the practical contradiction interpretation is a superset of these.
The FUL should show that actions that cannot possibly be universalized are prohibited, because those acts cannot be willed in 
a world where they are universalized. This property fails to hold in both raw DDL
and Kroy's formalization, but holds for my formalization. Showing that this property holds
for my formalization required significant logical background and the full code is presented in Appendix \ref{weirdtests}.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
representing a maxim and making it the input to the obligation operator, which only my implementation 
does. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
reasoning as demonstrated in Sections \nameref{joking} and \nameref{murderer}. Staying faithful to the philosophical 
literature enables my system to make more reliable judgements.

\medskip%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Conventional and Natural Acts} When arguing for the practical contradiction interpretation,
Korsgaard makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
A conventional act like promising relies on a convention, like the 
convention that a promise is a commitment, whereas a natural act is possible simply because of the laws 
of the natural world. It is easier to show the wrongness of conventional acts because there are worlds 
in which these acts are impossible; namely, worlds in which the convention does not exist. For example, 
the common argument against falsely promising is that if everyone were to falsely promise, the convention 
of promising would fall apart because people wouldn't believe each other, so falsely promising is prohibited. 
It is more difficult to show the wrongness of a natural act, like murder or violence. These acts can 
never be logically impossible; even if everyone murders or acts violently, murder and violence will 
still be possible, so it is difficult to show that they violate the FUL.

@@

FUL \citep{KorsgaardFUL}. I run this test in Chapter Applications, where I

@@

%:%167=85%:%

@@

%:%170=86%:%
%:%171=87%:%
%:%172=88%:%

@@

%:%180=95%:%
%:%181=96%:%
%:%182=97%:%

@@

%:%241=156%:%
%:%242=156%:%

@@

%:%245=158%:%

@@

%:%256=163%:%
%:%268=165%:%

@@

%:%320=218%:%
%:%321=218%:%

@@

%:%324=220%:%

@@

%:%328=223%:%

@@

%:%351=247%:%
%:%352=247%:%

@@

%:%355=249%:%

@@

%:%357=250%:%
%:%360=256%:%

@@

%:%372=268%:%
%:%373=268%:%

@@

%:%376=270%:%
%:%379=272%:%

@@

%:%413=306%:%
%:%414=306%:%

@@

%:%417=308%:%

@@

%:%419=309%:%

@@

%:%422=311%:%

@@

%:%425=313%:%

@@

%:%429=316%:%

@@

%:%434=321%:%
%:%435=321%:%

@@

%:%438=323%:%

@@

%:%440=324%:%

@@

%:%443=326%:%
%:%445=327%:%

@@

%:%455=331%:%
%:%467=333%:%

@@

%:%476=343%:%
%:%477=343%:%
%:%479=344%:%

@@

%:%485=349%:%

@@

%:%488=352%:%
%:%489=352%:%
%:%491=352%:%
%:%495=352%:%
%:%496=352%:%

@@

%:%498=353%:%
%:%499=353%:%
%:%508=355%:%

@@

%:%534=381%:%
%:%535=381%:%

@@

%:%538=383%:%

@@

%:%542=386%:%
%:%544=388%:%
%:%545=388%:%

@@

%:%548=390%:%

@@

%:%550=391%:%

@@

%:%553=393%:%

@@

%:%555=394%:%
%:%557=394%:%
%:%561=394%:%
%:%562=394%:%
%:%564=395%:%

@@

%:%580=403%:%

@@

@@

%:%601=423%:%
%:%603=425%:%

@@

%:%605=427%:%

@@

%:%616=431%:%
%:%628=433%:%
%:%629=434%:%
%:%630=435%:%

@@

%:%655=461%:%
%:%656=462%:%
%:%657=463%:%

@@

%:%663=468%:%
%:%664=469%:%
%:%665=470%:%

@@

%:%676=479%:%
%:%677=480%:%
%:%678=481%:%

@@

@@

%:%692=494%:%
%:%693=495%:%
%:%696=496%:%
%:%700=496%:%
%:%701=496%:%
%:%703=497%:%
%:%704=498%:%
%:%705=499%:%
%:%706=499%:%
%:%708=500%:%
%:%709=501%:%
%:%710=502%:%

@@

%:%717=503%:%
%:%720=504%:%
%:%721=505%:%
%:%722=505%:%
%:%723=506%:%
%:%726=507%:%
%:%730=507%:%
%:%731=507%:%
%:%733=508%:%
%:%734=509%:%
%:%744=511%:%
%:%745=512%:%
%:%746=513%:%

@@

@@

%:%767=533%:%
%:%768=534%:%
%:%771=535%:%
%:%775=535%:%
%:%776=535%:%
%:%777=535%:%
%:%779=536%:%
%:%785=536%:%
%:%788=537%:%
%:%789=538%:%
%:%790=538%:%
%:%791=539%:%
%:%792=540%:%
%:%795=541%:%
%:%799=541%:%
%:%800=541%:%
%:%801=541%:%
%:%803=542%:%
%:%804=543%:%
%:%805=544%:%
%:%815=546%:%
%:%816=547%:%
%:%817=548%:%

@@

%:%824=556%:%

@@

%:%828=557%:%
%:%832=557%:%
%:%833=557%:%
%:%835=558%:%
%:%836=559%:%
%:%837=560%:%
%:%847=562%:%
%:%848=563%:%
%:%849=564%:%

@@

@@

%:%856=570%:%
%:%857=571%:%
%:%858=572%:%
%:%861=573%:%
%:%865=573%:%
%:%866=573%:%
%:%867=573%:%
%:%869=574%:%
%:%870=575%:%
%:%871=576%:%
%:%881=578%:%
%:%882=579%:%

@@

%:%885=581%:%
%:%886=582%:%
%:%887=583%:%
%:%890=584%:%
%:%894=584%:%
%:%895=584%:%
%:%896=584%:%
%:%898=585%:%
%:%908=587%:%
%:%909=588%:%
%:%910=589%:%

@@

%:%925=604%:%
%:%926=605%:%
%:%927=606%:%

@@

%:%936=614%:%
%:%937=615%:%
%:%938=616%:%

@@

>>>>

The central unit of evaluation for Kantian ethics is a ``maxim,'' which Kant defines as ``the subjective 
principle of willing,'' or the principle that the agent understands themselves as acting on \citep{groundwork}. 
Modern Kantians differ in their interpretations of this definition. I adopt O'Neill's view, derived from 
Kant's example maxims, that a maxim includes the act, the circumstances, and the agent's purpose of 
acting or goal \citep{actingonprinciple}. Other potential views include Korsgaard's view, which omits 
the circumstances, and Kitcher's view, which adds a motivation \citep{actingforareason, kitcher}. I 
address the limitations of these approaches in Appendix \ref{maximmotive}.

@@

I implement this definition in Isabelle by defining the \texttt{type\_synonym} below for the type
of a maxim.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am strapped for cash, will falsely promise
to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
world when my bank account is empty. The second term represents the action, which is an open sentence
because different agents can perform a particular action. For example, the action, ``will falsely promise
to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
is true at the real world if I have successfully received easy cash.%
}%
\begin{isamarkuptext}%
O'Neill argues that a maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed \citep[37]{actingonprinciple}. 
She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
but instead in the pursuit of ends which it deems valuable. The inclusion a maxim's end is essential 
for the version of the FUL that I will implement, explained in Section \ref{praccon}.

O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
relevant circumstance for a particular maxim. This gives rise to ``the tailoring objection,'' 
under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection \cite{kitcher}.} For example, the maxim ``When my name is Jane Doe
and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job,'' 
is universalizable but is clearly a false positive because we think that murder for professional gain is wrong. 
One solution to this problem is to argue that the circumstance ``When my name is Jane Doe and I am wearing a 
purple shirt and it is Tuesday morning'' is not morally relevant 
to the act and goal. This solution requires determining what qualifies as a relevant circumstance.

@@

Another solution is to develop heuristics to classify circumstances as morally 
relevant. For example, one such attempt could define a moral closeness relation between an action, a 
goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
define some set of morally important entities, and classify morally relevant circumstances as those
that involve morally important entities. Determining morally relevant
circumstances, either using heuristics or human involvement, is a ripe area for future work.

@@

As an alternative to the logical contradiction view, Korsgaard endorses the practical contradiction view, 
which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
you commit yourself to the maxim's goal, and thus cannot rationally will that this goal be 
undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
loud children, then she cannot be secure in the possession of her life, because her own mother would 
have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
My above investigation of \texttt{FUL0} shows that if the FUL holds for badly formed maxims, then 
it is inconsistent. This is not only a logical property of my system, but it also has philosophical
significance that coheres with Korsgaard's and O'Neill's interpretations of a maxim as a practical
guide to action \citep{actingforareason,actingonprinciple}. A maxim is a practical principle that guides how we behave in everyday life. A 
principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast,'' is not 
practically relevant. No agent would ever need to act on such a principle. Morality helps agents decide
whether to act on a potential principle of action, but no agent would need to ask
``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" It is neither contradictory
nor prohibited, and it is the wrong kind of principle to be evaluating. It is not a
well-formed maxim, so the categorical imperative cannot apply to it.

@@

\includegraphics[scale=0.6]{goalstable.png}

@@

\noindent \textbf{Obligations Never Contradict} Contradictory obligations

@@

for rational agents. Ought implies can requires that obligations never contradict each other, because an agent 

@@

\noindent \textbf{Distributive Property for Obligations Holds} Another property related to contradictory obligations is the distributive property for the obligation

@@

\noindent \textbf{Prohibits Actions That Are Impossible to Universalize} Recall that 
the logical contradiction interpretation of the Formula of Universal Law prohibits lying because in a world 
where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
lie because the institution of lying and believing would break down. In Section \ref{praccon}, 
I recreated Korsgaard's argument for why the logical contradiction interpretation is weaker than what the
Formula of Universal Law should actually require. Therefore, any implementation of the FUL should be 
able to show that the actions prohibited by the logical contradiction interpretation are prohibited, 
because the set of actions prohibited by the practical contradiction interpretation is a superset of these.
The FUL should show that actions that cannot possibly be universalized are prohibited, because those acts cannot be willed in 
a world where they are universalized. This property fails to hold in both raw DDL
and Kroy's formalization, but holds for my formalization. Showing that this property holds
for my formalization required significant logical background and the full code is presented in Appendix \ref{weirdtests}.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Robust Representation of Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
representing a maxim and making it the input to the obligation operator, which only my implementation 
does. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
reasoning as demonstrated in Sections \nameref{joking} and \nameref{murderer}. Staying faithful to the philosophical 
literature enables my system to make more reliable judgements.

\medskip%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Can Prohibit Conventional and Natural Acts} When arguing for the practical contradiction interpretation,
Korsgaard makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
A conventional act like promising relies on a convention, like the 
convention that a promise is a commitment, whereas a natural act is possible simply because of the laws 
of the natural world. It is easier to show the wrongness of conventional acts because there are worlds 
in which these acts are impossible; namely, worlds in which the convention does not exist. For example, 
the common argument against falsely promising is that if everyone were to falsely promise, the convention 
of promising would fall apart because people wouldn't believe each other, so falsely promising is prohibited. 
It is more difficult to show the wrongness of a natural act, like murder or violence. These acts can 
never be logically impossible; even if everyone murders or acts violently, murder and violence will 
still be possible, so it is difficult to show that they violate the FUL.

@@

FUL \citep{ebelsduggan, KorsgaardFUL}. I run this test in Chapter Applications, where I

@@

%:%166=83%:%
%:%167=84%:%

@@

%:%170=88%:%
%:%171=88%:%

@@

%:%178=94%:%
%:%179=95%:%
%:%180=96%:%

@@

%:%240=155%:%
%:%242=157%:%

@@

%:%244=158%:%

@@

%:%249=162%:%
%:%257=164%:%

@@

%:%319=216%:%
%:%321=219%:%

@@

%:%323=220%:%

@@

%:%326=222%:%

@@

%:%350=245%:%
%:%352=248%:%

@@

%:%354=249%:%

@@

%:%357=251%:%
%:%358=251%:%

@@

%:%371=267%:%
%:%373=269%:%

@@

%:%375=270%:%
%:%377=271%:%

@@

%:%412=305%:%
%:%414=307%:%

@@

%:%416=308%:%

@@

%:%419=310%:%

@@

%:%422=312%:%

@@

%:%424=313%:%

@@

%:%427=315%:%

@@

%:%433=320%:%
%:%435=322%:%

@@

%:%437=323%:%

@@

%:%440=325%:%

@@

%:%443=327%:%
%:%444=327%:%

@@

%:%448=330%:%
%:%456=332%:%

@@

%:%475=341%:%
%:%477=344%:%
%:%478=344%:%

@@

%:%483=348%:%

@@

%:%487=351%:%
%:%489=353%:%
%:%490=353%:%
%:%492=353%:%
%:%496=353%:%

@@

%:%498=354%:%
%:%499=354%:%
%:%500=354%:%

@@

%:%533=380%:%
%:%535=382%:%

@@

%:%537=383%:%

@@

%:%540=385%:%
%:%543=387%:%
%:%545=389%:%

@@

%:%547=390%:%

@@

%:%550=392%:%

@@

%:%553=394%:%

@@

%:%555=395%:%
%:%556=395%:%
%:%558=395%:%
%:%562=395%:%
%:%563=395%:%

@@

%:%571=402%:%

@@

%:%599=422%:%

@@

%:%601=424%:%
%:%603=426%:%

@@

@@

%:%608=430%:%
%:%609=431%:%
%:%610=432%:%
%:%619=434%:%

@@

%:%653=458%:%
%:%654=459%:%
%:%655=460%:%

@@

%:%661=467%:%
%:%662=468%:%
%:%663=469%:%

@@

%:%673=478%:%
%:%674=479%:%
%:%675=480%:%

@@

%:%690=493%:%

@@

%:%692=495%:%
%:%694=497%:%
%:%695=497%:%
%:%696=498%:%
%:%699=499%:%
%:%703=499%:%
%:%704=499%:%
%:%706=500%:%
%:%707=501%:%
%:%708=502%:%
%:%709=502%:%

@@

%:%712=504%:%
%:%713=505%:%
%:%714=506%:%
%:%720=506%:%
%:%723=507%:%
%:%724=508%:%
%:%725=508%:%
%:%726=509%:%
%:%729=510%:%
%:%733=510%:%
%:%734=510%:%
%:%736=511%:%
%:%737=512%:%

@@

%:%765=532%:%

@@

%:%767=534%:%
%:%769=536%:%
%:%770=536%:%
%:%771=537%:%
%:%774=538%:%
%:%778=538%:%
%:%779=538%:%
%:%780=538%:%
%:%782=539%:%
%:%788=539%:%
%:%791=540%:%
%:%792=541%:%
%:%793=541%:%
%:%794=542%:%
%:%795=543%:%
%:%798=544%:%
%:%802=544%:%
%:%803=544%:%
%:%804=544%:%
%:%806=545%:%
%:%807=546%:%
%:%808=547%:%

@@

%:%823=554%:%
%:%824=555%:%

@@

%:%827=559%:%
%:%828=559%:%
%:%831=560%:%
%:%835=560%:%
%:%836=560%:%
%:%838=561%:%
%:%839=562%:%
%:%840=563%:%

@@

%:%854=569%:%

@@

%:%856=571%:%
%:%858=573%:%
%:%859=573%:%
%:%860=574%:%
%:%861=575%:%
%:%864=576%:%
%:%868=576%:%
%:%869=576%:%
%:%870=576%:%
%:%872=577%:%
%:%873=578%:%
%:%874=579%:%

@@

%:%885=582%:%
%:%887=584%:%
%:%888=584%:%
%:%889=585%:%
%:%890=586%:%
%:%893=587%:%
%:%897=587%:%
%:%898=587%:%
%:%899=587%:%
%:%901=588%:%

@@

%:%922=601%:%
%:%923=602%:%
%:%924=603%:%

@@

%:%933=612%:%
%:%934=613%:%
%:%935=614%:%

@@

%:%955=633%:%
%:%956=634%:%
%:%957=635%:%
